CommonMind Consortium: DLPFC

### 2020-10-13 combined_analysis/CTS/GABA.Rmd
drop genes that don't vary

library(githubr)
parentId = 'syn23241817';
activityName = 'Analysis of read count data by cohort: GABA';
activityDescription = 'Analysis of read count data by cohort: GABA';

thisFileName <- 'GABA.Rmd'

>>>>

library(githubr)
parentId = 'syn23241817';
activityName = paste('Analysis of read count data by cohort:', params$cellType)
activityDescription = paste('Analysis of read count data by cohort:', params$cellType)

thisFileName <- paste0(params$cellType, '.Rmd')

### 2020-10-13 combined_analysis/CTS/Glu.Rmd
drop genes that don't vary

library(githubr)
parentId = 'syn23241817';
activityName = 'Analysis of read count data by cohort: Glu';
activityDescription = 'Analysis of read count data by cohort: Glu';

thisFileName <- 'Glu.Rmd'

>>>>

library(githubr)
parentId = 'syn23241817';
activityName = paste('Analysis of read count data by cohort:', params$cellType)
activityDescription = paste('Analysis of read count data by cohort:', params$cellType)

thisFileName <- paste0(params$cellType, '.Rmd')

### 2020-10-13 combined_analysis/CTS/MgAs.Rmd
drop genes that don't vary

library(githubr)
parentId = 'syn23241817';
activityName = 'Analysis of read count data by cohort: MgAs';
activityDescription = 'Analysis of read count data by cohort: MgAs';

thisFileName <- 'MgAs.Rmd'

@@

>>>>

library(githubr)
parentId = 'syn23241817';
activityName = paste('Analysis of read count data by cohort:', params$cellType)
activityDescription = paste('Analysis of read count data by cohort:', params$cellType)

thisFileName <- paste0(params$cellType, '.Rmd')

@@

vobj.lst = lapply(vobj.lst, function(vobj){
  vobj[isexpr,]
  })
```

### 2020-10-13 combined_analysis/CTS/Olig.Rmd
drop genes that don't vary

library(githubr)
parentId = 'syn23241817';
activityName = 'Analysis of read count data by cohort: Olig';
activityDescription = 'Analysis of read count data by cohort: Olig';

thisFileName <- 'Olig.Rmd'

@@

vobj.lst = lapply(vobj.lst, function(vobj){
  vobj[isexpr,]
  })

>>>>

library(githubr)
parentId = 'syn23241817';
activityName = paste('Analysis of read count data by cohort:', params$cellType)
activityDescription = paste('Analysis of read count data by cohort:', params$cellType)

thisFileName <- paste0(params$cellType, '.Rmd')

@@

vobj.lst = lapply(vobj.lst, function(vobj){
  vobj[isexpr,]
  })
```
